---
title: "main"
author: "Yanwan Zhu"
date: "3/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
# Use the pre-processing script
source("pre-processing.R")
```


Right now, the pre-processing script only has two functions.

```{r sourced functions}
# Use functions to load and clean data
load_data() # creates two dataframes in the global environment
clean_data()
```

## Important: things to keep consistant!
- Put all 4 data files in a folder called `data`, because the pre-processing script refers to "data/..."
- `sale-listings`: the variable name for sale-listings
- `amenities`: the variable name for amenities, although we're not using it for now

## Exploratory Data Analysis
- `EDA_text_EY.Rmd`: EDA, data cleaning, bigram visualization

## Models

- `null_naive_ml.R`: null model using the mean price 
- `linear_reg_ml.Rmd`: linear regression models
- `decision_tree_analysis.Rmd`: decision tree and random forest models


