---
title: "main"
author: "Yanwan Zhu"
date: "3/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
# Use the pre-processing script
source("pre-processing.R")
source("text_processing.R")
```


Right now, the pre-processing script has four functions.

```{r sourced functions}

load_data() # creates two dataframes in the global environment

clean_data() # cleans the data

sale_listings_imputed <- impute_data() # imputes size values and returns a new dataframe

#ml_setup sometimes does not work
ml_setup(sale_listings_imputed) # splits the input data into test and training sets
```

```{r text processing}
#must run pre-processing up to impute_data before text processing
text_var() #create binary variables and sentiment score based on text features
```



```{r check imputation}
original <- ggplot(data=sale_listings_imputed, aes(x=size_sqft))+
  geom_density(color = "blue") +
  geom_vline(xintercept = mean(sale_listings$size_sqft, na.rm = TRUE), color="black", alpha=0.5)

log <- ggplot(data=sale_listings_imputed, aes(x=log(size_sqft)))+
  geom_density(color = "purple") +
  geom_density(aes(x=log(sale_listings$size_sqft)), color = "pink")+
  geom_vline(xintercept = mean(log(sale_listings_imputed$size_sqft)), color="black", alpha=0.5)

library(patchwork)
original / log
```


## Important: things to keep consistent!

- Put all 4 data files in a folder called `data`, because the pre-processing script refers to "data/..."
- `sale-listings`: the variable name for sale-listings
- `amenities`: the variable name for amenities, although we're not using it for now

## Exploratory Data Analysis
- `EDA_text_EY.Rmd`: EDA, data cleaning, bigram visualization

## Models

- `null_naive_ml.R`: null model using the mean price 
- `linear_reg_ml.Rmd`: linear regression models
- `decision_tree_analysis.Rmd`: decision tree and random forest models

## Grouping cities
```{r city_group}
median_price_city <- aggregate(sale_listings_imputed$price, by = list(sale_listings_imputed$major_city), median) %>%
  arrange(desc(x))

median_price_city$price_group <- cut(median_price_city$x, 10, include.lowest=TRUE,
                                     labels = seq(10,1))

city_group <- median_price_city%>%
  select(-x) %>%
  rename(major_city = Group.1,
         city_group = price_group)

sale_listings_imputed <- left_join(sale_listings_imputed, city_group, by ="major_city")
```


## Tables for final paper
### Initial list of variables
\begin{table}[]
\centering
\caption{Variables in the original data set provided by StreetEasy}
\label{intial_var}
\begin{tabular}{ll}
Variable                 & Definition                                 \\
id                       & Unique identifier for sale listing         \\
property\_id             & Unique identifier for property             \\
unittype                 & Property type                              \\
subject                  & Listing subject                            \\
listing\_description     & Listing description                        \\
bedrooms                 & Number of bedrooms                         \\
bathrooms                & Number of bathrooms                        \\
anyrooms                 & Total number of rooms                      \\
size\_sqft               & Square footage                             \\
price                    & Listed price                               \\
addr\_street             & Street                                     \\
addr\_unit               & Unit                                       \\
addr\_cross              & Cross streets                              \\
addr\_hood               & Neighborhood                               \\
addr\_city               & City                                       \\
addr\_state              & State                                      \\
addr\_zip                & Zip code                                   \\
addr\_lon                & Longitude                                  \\
addr\_lat                & Latitude                                   \\
time\_to\_subway         & Time to subway                             \\
half\_baths              & Number of half bath                        \\
census\_tract            & Census tract                               \\
census\_block            & Census block                               \\
building\_count          & Number of building(s)                      \\
floor\_count             & Number of floors in the building           \\
residential\_unit\_count & Number of residential unit in the building \\
total\_unit\_count       & Total number of units in the building      \\
year\_built              & Building year built                        \\
is\_historic             & Whether is a historic building             \\
landmark\_name           & Building landmark name                     \\
area\_name               & Area name                                 
\end{tabular}
\end{table}

### Unit type
```
"NONE         = ' '
CONDO        = 'D'
COOP         = 'P'
TOWNHOUSE    = 'T'
LOFT         = 'L'
CONDOP       = 'N'
HOUSE        = 'H'
MULTIFAMILY  = 'M'
RENTAL       = 'R'
UNKNOWN      = '?'
LAND         = 'A'
COMMERCIAL   = 'C'
MOBILE_HOME  = 'E'
BUILDING     = 'B'
ESTATE       = 'S'
APARTMENT    = 'F' # F is for Flat.
UNCLASSIFIED = 'U'
ANYHOUSE     = 'X'
AUCTION      = 'Z'
FRACTIONAL   = 'Y'"
```



### List of variables after pre-processing & var creation

```{r descriptive stats for numerical var}
descriptive_df <- sentiments_join %>%
  select(price, bedrooms, bathrooms, size_sqft, floor_count, score)
descriptive_num <- psych::describe(descriptive_df) %>%
  select(n, mean, sd, median, min, max)
psychTools::df2latex(descriptive_num)
```

```{r descriptive stats for cat var}
descriptive_df_cat <- sentiments_join %>%
  mutate(hw_floors = as.factor(hw_floors),
         stainless_steel= as.factor(stainless_steel),
         pet_friendly = as.factor(pet_friendly),
         wd = as.factor(wd))
furniture::table1(descriptive_df_cat, county, unittype, is_historic, city_group, hw_floors, stainless_steel, pet_friendly, wd, output = "latex2", na.rm = TRUE )
```

