---
title: "regression_LL"
output: html_document
---

```{r loading packages}
library(dplyr)
library(stringr)
library(rpart)
library(rattle)
library(ggplot2)
```

```{r loading files and joinging dataframes}
amenities <- read.csv("/Users/llow/Desktop/capstone/streeteasy_data/amenities.csv")
listings <- read.csv("/Users/llow/Desktop/capstone/streeteasy_data/sale_listings.csv")
joined <- full_join(amenities, listings, by = "property_id")
```

```{r cleaning data}
joined$size_sqft[joined$size_sqft == 0] <- NA
joined
listings$size_sqft[listings$size_sqft == 0] <- NA
listings
```


```{r comparing price to other variables to see if there is a correlation}
pairs(~bedrooms + bathrooms + size_sqft + price, data = listings,
   main="Simple Scatterplot Matrix",
   upper.panel = NULL)
```

```{r creating and plotting linear regression}
reg <- lm(price ~ bedrooms + bathrooms + size_sqft, data = listings)
summary(reg)
plot(reg)
```


1. shows that data may be better modeled by a parabola not a line
2. distribution is not normal and has lots of data on the tails
3. there is not equal variance between points
4. there are three major outliers that are screwing up this particular model
conclusion: this data should not be modeled linearly 

```{r lets try adding more variables}
reg_extra <- lm(price ~ bedrooms + bathrooms + size_sqft + year_built + floor_count + time_to_subway + half_baths, data = listings)
summary(reg_extra)
plot(reg_extra)
```
definitely shouldn't be modeled linearly...

```{r}
quad_reg <- lm(price ~ poly(bedrooms, 3) + poly(bathrooms, 2) + poly(floor_count, 2), data = listings)
summary(quad_reg)
plot(quad_reg)
```

```{r creating and plotting linear regression}
reg_test <- lm(price ~ bedrooms + area_name, data = listings)
summary(reg_test)
plot(reg_test)
```

looks like linear and polynomial regression is not the way to go.  let's try decision tree analysis:

```{r simple decision tree}
train = c(sample(1:50, 25), sample(51:100, 25), sample(101:150, 25))
tree = rpart(price ~ bedrooms + bathrooms + size_sqft + time_to_subway, data = listings, subset = train, method = "class")

fancyRpartPlot(tree)
```

```{r prediction analysis}
listings.Predict = predict(tree, listings, type = "class")
table(Prices = listings$price, Prediction = listings.Predict)
```

```{r eda}
avg_price <- mean(listings$price, na.rm = TRUE)
avg_price

avg_bed <- mean(listings$bedrooms, na.rm = TRUE)
avg_bed

avg_bath <- mean(listings$bathrooms, na.rm = TRUE)
avg_bath

avg_size <- mean(listings$size_sqft, na.rm = TRUE)
avg_size

avg_tts <- mean(listings$time_to_subway, na.rm = TRUE)
avg_tts

avg_halfb <- mean(listings$half_baths, na.rm = TRUE)
avg_halfb

avg_year <- mean(listings$year_built, na.rm = TRUE)
avg_year

common_city <- listings %>%
  group_by(addr_city) %>%
  count(addr_city, sort = TRUE) 
common_city

common_neigh <- listings %>%
  group_by(area_name) %>%
  count(area_name, sort = TRUE) 
common_neigh
```

```{r distributions of numeric variables}
price_plot <- ggplot(data = listings, aes(x = price)) + 
  geom_histogram()
price_plot

bed_plot <- ggplot(data = listings, aes(x = bedrooms)) + 
  geom_histogram()
bed_plot

bath_plot <- ggplot(data = listings, aes(x = bathrooms)) + 
  geom_histogram()
bath_plot

size_plot <- ggplot(data = listings, aes(x = size_sqft)) + 
  geom_histogram()
size_plot

tts_plot <- ggplot(data = listings, aes(x = time_to_subway)) + 
  geom_histogram()
tts_plot

year_plot <- ggplot(data = listings, aes(x = year_built)) + 
  geom_histogram()
year_plot

```





